### 2020-06-25 Documents/ESA/sections/Intro.tex
minor mods in intro
Updated ESA

    Swarm robotics bases its success upon the collaboration of many agents who contribute towards
    the overall success of the system \cite{Hamann2018}. The collaboration of many agents
    who share the same goal can give rise to behaviours that are far more complex than individual
    robots can achieve. The capacity for complexity is becoming increasingly important as robots are
    we are presented with ever more challenging tasks including: search and rescue, cleaning up
    space debris, and robotic assembly. Such tasks are beyond the capabilities of individual robots
    and so we must leverage the capacity for agents in a swarm to collectively achieve our
    goals. Fortunately, a growing subset of the Control Theory community have turned their attention
    towards this very problem and address the question: how does the dynamical behaviour of a
    population of agents change under the influence of control? Note that we use the term 'agent'
    loosely here, an agent can refer to anything from a simple particle \cite{Roy2017}
    to a complex robot \cite{Elamvazhuthi2019}. In answering this question, researchers have
    gained a stronger understanding of how a swarm may be controlled to achieve desired results.

    Another technique which has made incredible strides towards improving the capability of
    autonomous systems to communally achieve results is Multi-Agent Reinforcement Learning (MARL)
    \cite{SchwartzMulti-agentApproach}. This builds on the ideas of classical Reinforcement Learning which allows an
    agent to optimise its strategies towards tackling a task through repeated exposure to that task.
    MARL utilises this same principle with the caveat that agents must adapt their strategies based
    not only on the outcome of the action, but also on the actions of the other agents. This has
    shown strong results in practical applications \cite{Woolridge2009, SchwartzMulti-agentApproach, Yang2004}. Whilst MARL was
    once considered to be non-identifiable (there is no clear way of identifying the algorithm that
    a particular agent was trained on) and black box (there is no clear way of ensuring a desired
    result from a learning algorithm), a steady stream of research is emerging to lift this fog
    \cite{Bloembergen2015}. This allows for researchers to choose the parameters of their learning
    algorithms appropriately to ensure that learning agents behave in the desired manner.

@@

    \begin{enumerate}
    	\item A population of robots is given a goal which must be achieved, which can often be
    	deconstructed into a set of smaller tasks, to be executed simultaneously. 
    	\item These are to be performed in a dynamic environment with obstacles present and where
    	the number of tasks, and their priorities may be in constant flux.
    	\item The agents in the system must, therefore, make decisions collectively which will in
    	the system achieving the given goals. Due to the dynamic quality of the problem, these
    	decisions may need to be evaluated online and in a decentralised fashion, as it may not be
    	possible for a centralised decision maker to communicate with all agents.
    	\item It is desirable, therefore, to control the dynamical behaviour of
    	a system composed of agents who learn and adapt through interactions with each other. In
    	addition, to ensure the safe operation of the system, properties such as state and control
    	constraints must be satisfied.
    \end{enumerate}

>>>>

    Swarm robotics bases its success upon the collaboration of many agents who contribute towards
    the overall success of the system \cite{Hamann2018}. The collaboration of many agents who share
    the same goal can give rise to behaviours that are far more complex than individual robots can
    achieve. The capacity for complexity is becoming increasingly important as robots are we are
    presented with ever more challenging tasks including: search and rescue, cleaning up space
    debris, and robotic assembly. Such tasks are beyond the capabilities of individual robots and so
    we must leverage the capacity for agents in a swarm to collectively achieve our goals.
    Fortunately, a growing subset of the Control Theory community have turned their attention
    towards this very problem and address the question: how does the dynamical behaviour of a
    population of agents change under the influence of control? Note that we use the term `agent'
    loosely here, an agent can refer to any entity to which controls may be applied, from a simple
    particle \cite{Roy2017} to a complex robot \cite{Elamvazhuthi2019}. In answering this question,
    researchers have gained a stronger understanding of how a swarm may be controlled to achieve
    desired results.

    Another technique which has made incredible strides towards improving the capability of
    autonomous systems to communally achieve results is Multi-Agent Reinforcement Learning (MARL)
    \cite{SchwartzMulti-agentApproach}. This builds on the ideas of classical Reinforcement Learning
    which allows an agent to optimise its strategies towards tackling a task through repeated
    exposure to that task. MARL utilises this same principle with the caveat that agents must adapt
    their strategies based not only on the outcome of the action, but also on the actions of the
    other agents. This has shown strong results in practical applications \cite{Woolridge2009,
    SchwartzMulti-agentApproach, Yang2004}. Whilst MARL was once considered to be non-identifiable
    (there is no clear way for a third party to identify the algorithm that a particular agent was
    trained on) and black box (there is no clear way of ensuring a desired result from a learning
    algorithm from its behaviour during and after learning), a steady stream of research is emerging
    to lift this fog \cite{Bloembergen2015}. This allows for researchers to choose the parameters of
    their learning algorithms appropriately to ensure that learning agents behave in the desired
    manner.

@@

    \begin{enumerate}
    	\item A population of robots is given a goal which must be achieved, which can often be
    	deconstructed into a set of smaller tasks, to be executed simultaneously. 
    	\item These are to be performed in a dynamic environment with obstacles present and where
    	the number of tasks, and their priorities may be in constant flux.
    	\item The agents in the system must, therefore, make decisions collectively which will result
        in the system achieving the given goals. Due to the dynamic quality of the problem, these
        decisions may need to be evaluated online and in a decentralised fashion, as it may not be
        possible for a centralised decision maker to communicate with all agents. 
        \item It is desirable, therefore, to control the dynamical behaviour of
    	a system composed of agents who learn and adapt through interactions with each other. In
    	addition, to ensure the safe operation of the system, properties such as state and control
    	constraints must be satisfied.
    \end{enumerate}

### 2020-06-25 Documents/ESA/sections/LitReview.tex
Updated ESA

    \item Distributed. It will often be the case that a multi-agent system must spread out across a
    large area or operate in regions where communication is limited. As such it is beneficial that
    such a system does not rely too heavily on communication with a central body. The individual
    agents must, therefore, be able to make their own decisions and act as independent entities.
    Aside from the advantage of communication, this ensures that the system is not tied to a single
    point of failure; in a system governed by a centralised decision maker, any faults in the
    central body propagates throughout the group. Of course, this comes at the price of
    computational load - if the agents are required to act independently, they must possess the
    resources to do so. The term distributed should not be confused with decentralised. The latter
    refers to a regime in which agents all communicate with one another before making a decision.
    Whilst this is preferable to a centralised decision maker in terms of the requirement for one
    entity to communicate with all agents, it still places a high cost on the requirement that
    agents be in constant communication with one another. In fact it may pose the additional risk
    that if any agent in the team fails, the whole pipeline falls apart. Distributivity, on the
    other hand, requires that agents make independent decisions so that, though agents may
    communicate with each other, they are still able to operate when this is not possible.
    \item Generality. MAS come in many different flavours; sometimes a small group of heterogeneous 
    (agents with different capabilities) agents may be required to perform a delicate task whilst
    in others, it may be required that a large population of homogeneous (all of the same type)
    agents perform multiple tasks simultaneously. Indeed the same MAS may have to adapt its
    strategy whilst in the middle of a task. It would be a hindrance if the agents were required to
    be reprogrammed with a completely different control methodology each time the situation changes
    slightly. It would be preferable if the method could apply to all different types of scenarios,
    with homogenous or heteregeneous agents, with single tasks or multiple, in any environment with
    only minor customisation required. Better still if the agents are able to adapt themselves to
    the specifics of the scenario.
    \item Low Computational Load. As mentioned in the previous chapter, a MAS will often be used in
    complex situations, many of which will be too dangerous for human intervention. As such, the
    system will be required to carry out its tasks online. For this reason, it is vital that the
    control method be one which produces low computational load - especially where the time frame
    for adjusting agent behaviour is limited. Monetary concerns also play a part in this metric; it
    would not do to impose that every member of the team be equipped with high performance computing
    power as this would likely fall outside of the budget of any practical usage.
    \item Robustness. Particularly for physical robots, a MAS should be able to operate in
    situations which present sensor noise, communication noise, latency, and environmental
    disturbances. This is rather important in unseen environments where full a priori knowledge of
    the map cannot be assumed.
    \item Scalable. This is mentioned last since the ability for a MAS to scale comes from its
    distributivity  and low computational load. Scalability is the capacity for any method of

@@

    always required that a MAS be formed of dozens (or even hundreds) of agents. Depending on the
    task at hand (e.g. robotic surgery), it may be beneficial for fewer, more capable agents to
    perform the task, rather than a large population. 

@@

Game Theory has a rich history when considering an understanding of multi-agent systems and it
is impossible to examine MAS without an understanding of Game Theory. These
begin in economics but have found a strong application in computation due to the rising need for
distributed systems. Game Theory, therefore, branches across all of the categories in this
chapter although its synergy with swarms requires development) since Dec-POMDP
and MARL methods have both base their theory upon the foundations of Game Theory.

@@

Similarly Bayesian Games is a game theoretic approach with incomplete information (thus it is
sometimes referred to as an ‘incomplete information game’). This allows for a POSG to be
approximated by a sequence of smaller, more tractable games
\cite{Emery-Montemerlo}. However, iterating through the entire team of agents to
find an optimal solution is a lengthy process and does not allow for immediate actions in dynamic
situations. To address this, \cite{Ray2010} propose to place distinct payoffs on each
agent and to consider team formation based on social hierarchy as well as preferred partners. This
allows the complexity of the problem to be broken down into smaller game units and also provides a
clear order in which the games are to be played. This minimises the interference across robots and
allows for more immediate action to be taken by agents who choose their strategy early on, while
leaving more passive tasks for those later in the sequence.

The Bayesian Game formulation therefore provides a strong candidate for rapid task re-allocation and
dynamic decision making. However, as found by Dai et. al \cite{Dai2018} this is
conditional on an understanding by each robot of the strategy of others, which in turn requires
adequate communication between robots. Therefore, the game theoretical formulation will fail where
communication is not possible amongst team members. However, the addition of heuristics, such as
deep learning, may be able to advance an agent’s ability to recognise the strategies taken by other
members of its team without the need for significant explicit communication.

@@

This idea is explored in \cite{Marden2018AnnualControl}. Here, a zero-sum game is considered in
which the players are a controller and an adversarial environment. The design of the controller must
be such that it is able to drive the system to zero error. To illustrate, consider the problem of
designing a controller for a re-entry vehicle, as in \cite{Breitner1994ReentryGame}, in which
vortices seek to destabilise the agent. This will allow us to build stable agents in a much more
efficient manner since we can simulate the adversarial environment and hypothetical scenarios the
agent may encounter without actually encountering them. The same notion is explored by Bardi et al
\cite{Bardi1991DifferentialDisturbances}.

Mylvaganam et al, in \cite{Mylvaganam2017AutonomousApproach}, consider the N-robot collision
avoidance problem, similarly from the point of view of differential game theory. They develop a
robust feedback system for the robots which they show to be able to drive the system towards
predefined targets whilst providing guarantees of interference from other agents (or lack thereof).
In \cite{MylvaganamASystems}, Mylvaganam also considers a game theoretic control of multi-agent
systems in a distributed manner. Here, agents only consider their own payoff structure and have
limited communication with one another. The author shows that an approximate equilibrium can be
found using algebraic methods and illustrate the capabilities of the technique using a collision
avoidance example. For the sake of brevity the numerous contributions that Mylvaganam has made to
this field is not presented here. However, we will conclude with those presented in
\cite{Mylvaganam2014}. Here, the author presents approximate solutions to a number of differential
games, including linear-quadratic differential games (in which system dynamics are linear functions
whilst payoff functions are quadratic), Stackelberg differential games, where a hierarchy is 
induced across the players (a notion was suggested in the research proposal) and mean-field games,
which is discussed in 'MARL'. The importance of the linear-quadratic
differential game is the stability of the solution; solutions for the Nash equilibria (NE) are
admissable iff they are locally exponentially stable (which the author often shows with the aid of
Lyapunov functions). Approximate solutions to the NE are developed which are more feasible to
calculate online. The author then shows that this is not simply a theoretical exercise by applying
the novel methods towards multi-agent collision problems and designs dynamic control laws which
guarantee that each agent will reach their desired state whilst avoiding collision with the other
agents. Similarly, the Stackelberg game is applied to the problem of optimal monitoring by a multi
robot system.

@@

There are a number of approaches towards control systems. However, the interest of this review lies
in multi-agent systems which must operate in the face of uncertainty. As such, we focus on
stochastic and distributed control. The literature of the control communnity is vast and can be
divided into a number of sub-fields. We consider Distributed MPC (DMPC) and Swarm Optimal Control as
those which are particularly relevant to this study and review them in this section.

\subsection{Distributed Model Preodictive Control} \label{sec::Distributed_MPC}

Rawlings et al \cite{rawlings2017model} divide the problem of distributed control into four distinct
categories: decentralised control, non-cooperative control, cooperative control, and centralised
control. The last of these is not considered in the text since it only considers the case in which a
centralised controller has access and can manipulate multiple agents at once.

@@

The above models come under the term ‘mean-field models’ \cite{Elamvazhuthi2019b}, a series of
equations for stochastic forward processes (such as swarm foraging) in which, as the number of
agents tends to infinity, the true macroscopic motion of the system tends to these equations.
Importantly, however, these stochastic equations allow for an analysis of the swarm, as well as the
ability to develop control laws. In \cite{Li2017}, Li et al show that these models can be used to
develop control laws for robots in a swarm and drive them towards a target distribution. The method
is shown to perform accurately both in simulation and on real robots. The advantage is that
guarantees can be placed on the convergence and stabilisabiilty of the swarm towards the desired
distribution. However, there appears to be significant scope to expand upon this methodology from a
safety perspective. To begin with, the method does not consider inter-agent interactions and
therefore does not formally guard against collisions. In \cite{Inoue2019}, a similar problem is
considered, although collisions are avoided by having the robot simply move in the opposite
direction when encountering an obstacle. It is here that the mean-field models are not as strong
since they do not take these local interactions into account. It must be noted, however, that Inoue
et al have identified this problem and are currently working towards its incorporation into the
model.

>>>>

    \item \textbf{Distributed}. It will often be the case that a multi-agent system must spread out
across a large area or operate in regions where communication is limited. As such it is beneficial
that such a system does not rely too heavily on communication with a central body. The individual
agents must, therefore, be able to make their own decisions and act as independent entities. Aside
from the low communication load, this ensures that the system is not tied to a single point of
failure; in a system governed by a centralised decision maker, any faults in the central body
propagates throughout the group. Of course, this comes at the price of computational load - if the
agents are required to act independently, they must possess the resources to do so. The term
distributed should not be confused with decentralised. The latter refers to a regime in which agents
all communicate with one another before making a decision. Whilst this is preferable to a
centralised decision maker in terms of the requirement for one entity to communicate with all
agents, it still places a high cost on the requirement that agents be in constant communication with
one another. In fact it may pose the additional risk that if any agent in the team fails, the whole
pipeline falls apart. Distributivity, on the other hand, requires that agents make independent
decisions so that, though agents may communicate with each other, they are still able to operate
when this is not possible.
    \item \textbf{Generality}. MAS come in many different flavours; sometimes a small group of
heterogeneous  (agents with different capabilities) agents may be required to perform a delicate
task whilst in others, it may be required that a large population of homogeneous (all of the same
type) agents perform multiple tasks simultaneously. Indeed the same MAS may have to adapt its
strategy whilst in the middle of a task. It would be a hindrance if the agents were required to be
reprogrammed with a completely different control methodology each time the situation changes
slightly. It would be preferable if the method could apply to all different types of scenarios, with
homogenous or heteregeneous agents, with single tasks or multiple, in any environment with only
minor customisation required. Better still if the agents are able to adapt themselves to the
specifics of the scenario.
    \item \textbf{Low Computational Load}. As mentioned in the previous chapter, a MAS will often be
used in complex situations, many of which will be too dangerous for human intervention. As such, the
system will be required to carry out its tasks online. For this reason, it is vital that the control
method be one which produces low computational load - especially where the time frame for adjusting
agent behaviour is limited. Monetary concerns also play a part in this metric; it would not do to
impose that every member of the team be equipped with high performance computing power as this would
likely fall outside of the budget of any practical usage.
    \item \textbf{Robustness}. Particularly for physical robots, a MAS should be able to operate in
situations which present sensor noise, communication noise, latency, and environmental disturbances.
This is rather important in unseen environments where full a priori knowledge of the map cannot be
assumed.
    \item \textbf{Scalable}. This is mentioned last since the ability for a MAS to scale comes from
its distributivity  and low computational load. Scalability is the capacity for any method of

@@

always required that a MAS be formed of dozens (or even hundreds) of agents. Depending on the task
at hand (e.g. robotic surgery), it may be beneficial for fewer, more capable agents to perform the
task, rather than a large population. 

@@

Game Theory has a rich history when considering an understanding of multi-agent systems and it is
impossible to examine MAS without an understanding of Game Theory. These begin in economics but have
found a strong application in computation due to the rising need for distributed systems. Game
Theory, therefore, branches across all of the categories in this chapter although its synergy with
swarms requires development) since Dec-POMDP (Decentralised Partial Observable Markov Decision
Processes) and MARL methods have both base their theory upon the foundations of Game Theory.

@@

Similarly Bayesian Games is a game theoretic approach with incomplete information (thus it is
sometimes referred to as an `incomplete information game’). This allows for a POSG to be
approximated by a sequence of smaller, more tractable games
\cite{Emery-Montemerlo}. However, iterating through the entire team of agents to
find an optimal solution is a lengthy process and does not allow for immediate actions in dynamic
situations. To address this, \cite{Ray2010} propose to place distinct payoffs on each
agent and to consider team formation based on social hierarchy as well as preferred partners. This
allows the complexity of the problem to be broken down into smaller game units and also provides a
clear order in which the games are to be played. This minimises the interference across robots and
allows for more immediate action to be taken by agents who choose their strategy early on, while
leaving more passive tasks for those later in the sequence.

The Bayesian Game formulation therefore provides a strong candidate for rapid task re-allocation and
dynamic decision making. However, as found by Dai et al. \cite{Dai2018} this is
conditional on an understanding by each robot of the strategy of others, which in turn requires
adequate communication between robots. Therefore, the game theoretical formulation will fail where
communication is not possible amongst team members. However, the addition of heuristics, such as
deep learning, may be able to advance an agent’s ability to recognise the strategies taken by other
members of its team without the need for significant explicit communication.

@@

This idea is explored in \cite{Marden2018AnnualControl}. Here, a zero-sum game is considered in
which the players are a controller and an adversarial environment. The design of the controller must
be such that it is able to drive the system to zero error. To illustrate, consider the problem of
designing a controller for a re-entry vehicle, as in \cite{Breitner1994ReentryGame}, in which
vortices seek to destabilise the agent. This will allow us to build stable agents in a much more
efficient manner since we can simulate the adversarial environment and hypothetical scenarios the
agent may encounter without actually encountering them. The same notion is explored by Bardi et al.
\cite{Bardi1991DifferentialDisturbances}.

Mylvaganam et al, in \cite{Mylvaganam2017AutonomousApproach}, consider the N-robot collision
avoidance problem, similarly from the point of view of differential game theory. They develop a
robust feedback system for the robots which they show to be able to drive the system towards
predefined targets whilst providing guarantees of interference from other agents (or lack thereof).
In \cite{MylvaganamASystems}, Mylvaganam also considers a game theoretic control of multi-agent
systems in a distributed manner. Here, agents only consider their own payoff structure and have
limited communication with one another. The author shows that an approximate equilibrium can be
found using algebraic methods and illustrate the capabilities of the technique using a collision
avoidance example. For the sake of brevity the numerous contributions that Mylvaganam has made to
this field is not presented here. However, we will conclude with those presented in
\cite{Mylvaganam2014}. Here, the author presents approximate solutions to a number of differential
games, including linear-quadratic differential games (in which system dynamics are linear functions
whilst payoff functions are quadratic), Stackelberg differential games, where a hierarchy is 
induced across the players (a notion was suggested in the research proposal) and mean-field games,
which is discussed in `MARL'. The importance of the linear-quadratic
differential game is the stability of the solution; solutions for the Nash equilibria (NE) are
admissable iff they are locally exponentially stable (which the author often shows with the aid of
Lyapunov functions). Approximate solutions to the NE are developed which are more feasible to
calculate online. The author then shows that this is not simply a theoretical exercise by applying
the novel methods towards multi-agent collision problems and designs dynamic control laws which
guarantee that each agent will reach their desired state whilst avoiding collision with the other
agents. Similarly, the Stackelberg game is applied to the problem of optimal monitoring by a multi
robot system.

@@

There are a number of approaches towards control systems. However, the interest of this review lies
in multi-agent systems which must operate in the face of uncertainty. As such, we focus on
stochastic and distributed control. The literature of the control community is vast and can be
divided into a number of sub-fields. We consider Distributed MPC (DMPC) and Swarm Optimal Control as
those which are particularly relevant to this study and review them in this section.

\subsection{Distributed Model Predictive Control} \label{sec::Distributed_MPC}

Rawlings et al. \cite{rawlings2017model} divide the problem of distributed control into four distinct
categories: decentralised control, non-cooperative control, cooperative control, and centralised
control. The last of these is not considered in the text since it only considers the case in which a
centralised controller has access and can manipulate multiple agents at once.

@@

The above models come under the term ‘mean-field models’ \cite{Elamvazhuthi2019b}, a series of
equations for stochastic forward processes (such as swarm foraging) in which, as the number of
agents tends to infinity, the true macroscopic motion of the system tends to these equations.
Importantly, however, these stochastic equations allow for an analysis of the swarm, as well as the
ability to develop control laws. In \cite{Li2017}, Li et al. show that these models can be used to
develop control laws for robots in a swarm and drive them towards a target distribution. The method
is shown to perform accurately both in simulation and on real robots. The advantage is that
guarantees can be placed on the convergence and stabilisabiilty of the swarm towards the desired
distribution. However, there appears to be significant scope to expand upon this methodology from a
safety perspective. To begin with, the method does not consider inter-agent interactions and
therefore does not formally guard against collisions. In \cite{Inoue2019}, a similar problem is
considered, although collisions are avoided by having the robot simply move in the opposite
direction when encountering an obstacle. It is here that the mean-field models are not as strong
since they do not take these local interactions into account. It must be noted, however, that Inoue
et al. have identified this problem and are currently working towards its incorporation into the
model.

### 2020-06-25 Documents/ESA/sections/ProposedResearch.tex
Updated ESA

	This chapter describes a proposed line of research which aims to study the evolution of swarm
	systems with independent, learning agents under the influence of predictive controls. We detail
	the novel lines of research which this work aims to undertake, providing suggestions of the
	hypotheses posed by these lines. With this in mind the following studies are proposed and
	developed subsequently:

@@

    \begin{figure}[h]
    	\centering
    	\includegraphics[width=1.1\textwidth]{Figures/DynamicalBehaviours}
    	\caption{ \label{fig::DynamicalBehaviours} Different types of dynamial behaviour displayed
    	by learning agents. a)
    	Convergence
    	to a unique fixed point in the upper right corner (1, 1). This fixed point is unique, in
    	that all trajectories, regardless of initialisation, will converge to this point 
    	\cite{Tuyls2006AnGames}. b) Limit Cycle, the trajectories converge to cyclic behaviour c,
    	d) Chaotic behaviour, here small deviatons in the initial conditions can grow
    	exponentially \cite{Sanders2018}.}
    \end{figure}

@@

	Here, $\alpha$ and $\tau$ are the parameters of the agent; Sanders et al. refer to these as the
	memory and intensity of choice parameters respectively. Agent 1 takes action i with probability
	$x_i$ while Agent 2 takes action j with probability $y_j$. If these actions are taken, the agents
	receive payoff $a_{ij}$ and $b_{ji}$ respectively. With these equations, it is possible to
	predict the expected behaviour of Q-Learning agents, as shown in Figure 
	\ref{fig::TuylsExperiments}.

@@

	With this in mind, the intention of this area of study is to consider the analysis presented in
	works such as \cite{Sanders2018} and \cite{Galla2011}. Here, the authors examine the
	Experience Weighted Attraction (EWA) algorithm, which is regarded as a strong model for the
	learning behaviour of human players in a game \cite{Camerer2009}. The authors are able to
	determine the regions of parameter space in which complex behaviour,
	including cycles and chaos, predominantly occur and those in which a given game converges to a
	stable equilibrium. Figure \ref{fig::GallaPredictions} reproduces the graphs shown in \cite{Sanders2018} which
	illustrates the successful derivation of a 'phase line', across which learning shifts from
	convergent to chaotic.

@@

    Yet it can be argued that, for large populations of agents (e.g. a crowd), the aggregate
    behaviour may be predictable. This intuition is the foundation upon which crowd dynamics and
    flocking systems are based. In fact, the work presented by Leung et al. \cite{Hu2019} provides a
    cursory verification of this intuition. Here, the authors present an anaysis of the learning
    dynamics for a large agent population (which they approximate as containing infinite agents)
    where each agent is an independent Q-Learning using Boltzmann action selection. The
    result is a system of equations, governed by a Fokker-Planck model which is numerical shown to be a 
    strong predictor of the overall strategy selection of the population. Indeed, rather than
    examining the strategies of every agent in the population (which the authors approximate as
    infinitely large), they model the evolution of a probability density function which, for each
    action, defines the density of agents who retain a given Q-value for that action. This is
    illustrated in Figure \ref{fig::LeungPredictions}.

    \begin{figure}[h]
    	\centering
    	\includegraphics[width=0.9\textwidth]{Figures/LeungPredictions}
    	\caption{ \label{fig::LeungPredictions} Results as produced in Leung et al \cite{Hu2019}.
    	Here, the solid and dotted lines represent the evolution of thhe expectation of Q-values of
    	two actions across a population of 50 or 999 agents respectively who are trained on an
    	iterated Stag Hunt game. The circled and crossed
    	lines represent the dynamics of these Q-values as predicted by the system of equations
    	derived in the paper. These are seen to closely match the results of the numerical
    	experiments.}
    \end{figure}

@@

    As described in the previous chapter, the control of swarms has been examined through the use of
    mean field models. These models resolve the fact that it is impossible to view the entire system
    as simply the sum of all of the agents and rather model the overall state of the system through
    density functions. Controls are then applied to this function whose evolution is described
    through, typically, one of two partial differential equations: the Fokker-Planck Equation (also
    referred to as the Kolmogorov Forward Equation) and the Vlasov Equation. The former has seen
    some success in recent literature \cite{Elamvazhuthi2019, Li2017,
    Roy2017}, though it makes the assumption that the system evolves through 'drifted
    brownian motion'. This means that the agents are considered to move about independently and
    randomly, though under the influence of a field which affects their velocity. This technique
	has been shown, both theoretically and experimentally, to drive swarm systems in a stable
	manner \cite{Fleig}. The latter is beginning to show promise 
	though control is typically through leadership rather than fields \cite{Burger2019}.

@@

	\begin{itemize}
		\item The stablity of the system: Under what conditions is it possible to drive the
		swarm from one configuration to another in a stable manner? Fortunately, Bellomo et al
		present a candidate lyapunov functional upon which dissipation can be evaluated, though it
		will need to be adapted for the consideration of the consensus models.
		\item The guarantees of the system: Is it possible to ensure that controls remain within an
		admissible set (typically a closed, bounded and convex set \cite{Fredi2010}).
		\item Whether the conservation laws of normalisation and total mass, as presented in 
		\cite{Bellomo2017} can be guaranteed.
	\end{itemize}

@@

	A possible extension of this would be to consider online learning by incorporating the time
	evolution of the strategy space within the social interaction term, which would now be
	time-varying. The proper integration of these dynamical systems would depend on the form of the
	systems derived in Section \ref{sec::Large_Agent_Dynamics} and it is likely that relaxations would
	be required in terms of controllability results. A likely relaxation would be to examine only the
	behaviour in the long-enough time frame, which means that we could not impose a final time. Of
	course, this means that we could only consider optimal control rather than model predictive.
	However, without establishing the models from Section \ref{sec::Large_Agent_Dynamics}, this
	extension is speculative and it is likely that such an extension would fall outside the scope of
	the PhD.

>>>>

	This chapter describes a proposed line of research which aims to study the evolution of swarm
	systems with learning agents under the influence of predictive controls. We detail
	the novel lines of research which this work aims to undertake, providing suggestions of the
	hypotheses posed by these lines. With this in mind the following studies are proposed and
	developed subsequently:

@@

    \begin{figure}[h]
    	\centering
    	\includegraphics[width=1.1\textwidth]{Figures/DynamicalBehaviours}
    	\caption{ \label{fig::DynamicalBehaviours} Different types of dynamial behaviour
       displayed
    	by learning agents. a) Figure drawn from \cite{Tuyls2006AnGames}.
    	Convergence
    	to a unique fixed point in the upper right corner (1, 1). This fixed point is unique, in
    	that all trajectories, regardless of initialisation, will converge to this point. b) Limit Cycle, the trajectories converge to cyclic behaviour c,
    	d) Chaotic behaviour, here small deviatons in the initial conditions can grow
    	exponentially. b-d drawn from \cite{Sanders2018}}
    \end{figure}

@@

	Here, $\alpha$ and $\tau$ are the parameters of the agent; Sanders et al. refer to these as the
	memory and intensity of choice parameters respectively. Agent 1 takes action $i$ with probability
	$x_i$ while Agent 2 takes action $j$ with probability $y_j$. If these actions are taken, the agents
	receive payoff $a_{ij}$ and $b_{ji}$ respectively. With these equations, it is possible to
	predict the expected behaviour of Q-Learning agents, as shown in Figure 
	\ref{fig::TuylsExperiments}.

@@

	With this in mind, the intention of this area of study is to consider the analysis presented in
	works such as \cite{Sanders2018} and \cite{Galla2011}. Here, the authors examine the
	Experience Weighted Attraction (EWA) algorithm, which is regarded as a strong model for the
	learning behaviour of human players in a game \cite{Camerer2009}. The authors are able to
	determine the regions of parameter space in which complex behaviour,
	including cycles and chaos, predominantly occur and those in which a given game converges to a
	stable equilibrium. Figure \ref{fig::GallaPredictions} reproduces the graphs shown in \cite{Sanders2018} which
	illustrates the successful derivation of a `phase line', across which learning shifts from
	convergent to chaotic.

@@

    Yet it can be argued that, for large populations of agents (e.g. a crowd), the aggregate
    behaviour may be predictable. This intuition is the foundation upon which crowd dynamics and
    flocking systems are based. In fact, the work presented by Leung et al. \cite{Hu2019} provides a
    cursory verification of this intuition. Here, the authors present an anaysis of the learning
    dynamics for a large agent population (which they approximate as containing infinite agents)
    where each agent is an independent Q-Learner using Boltzmann action selection. The
    result is a system of equations, governed by a Fokker-Planck model which is numerical shown to be a 
    strong predictor of the overall strategy selection of the population. Indeed, rather than
    examining the strategies of every agent in the population (which the authors approximate as
    infinitely large), they model the evolution of a probability density function which, for each
    action, defines the density of agents who retain a given Q-value for that action. This is
    illustrated in Figure \ref{fig::LeungPredictions}.

    \begin{figure}[h]
    	\centering
    	\includegraphics[width=0.9\textwidth]{Figures/LeungPredictions}
    	\caption{ \label{fig::LeungPredictions} Results as produced in Leung et al. \cite{Hu2019}.
    	Here, the solid and dotted lines represent the evolution of the expectation of Q-values of
    	two actions across a population of 50 or 999 agents respectively who are trained on an
    	iterated Stag Hunt game. The circled and crossed
    	lines represent the dynamics of these Q-values as predicted by the system of equations
    	derived in the paper. These are seen to closely match the results of the numerical
    	experiments.}
    \end{figure}

@@

    As described in Chapter \ref{ch::Lit_Review}, the control of swarms has been examined through the
    use of
    mean field models. These models resolve the fact that it is impossible to view the entire system
    as simply the sum of all of the agents and rather model the overall state of the system through
    density functions. Controls are then applied to this function whose evolution is described
    through, typically, one of two partial differential equations: the Fokker-Planck Equation (also
    referred to as the Kolmogorov Forward Equation) and the Vlasov Equation. The former has seen
    some success in recent literature \cite{Elamvazhuthi2019, Li2017,
    Roy2017}, though it makes the assumption that the system evolves through 'drifted
    brownian motion'. This means that the agents are considered to move about independently and
    randomly, though under the influence of a field which affects their velocity. This technique
	has been shown, both theoretically and experimentally, to drive swarm systems in a stable
	manner \cite{Fleig}. The latter is beginning to show promise 
	though control is typically through leadership rather than fields \cite{Burger2019}.

@@

	\begin{itemize}
		\item The stablity of the system: Under what conditions is it possible to drive the
		swarm from one configuration to another in a stable manner? Fortunately, Bellomo et al.
		present a candidate lyapunov functional upon which dissipation can be evaluated, though it
		will need to be adapted for the consideration of the consensus models.
		\item The guarantees of the system: Is it possible to ensure that controls remain within an
		admissible set (typically a closed, bounded and convex set \cite{Fredi2010}).
		\item Whether the conservation laws of normalisation and total mass, as presented in 
		\cite{Bellomo2017} can be guaranteed.
	\end{itemize}

@@

	A possible extension of this would be to consider online learning by incorporating the time
	evolution of the strategy space within the social interaction term, which would now be
	time-varying. The proper integration of these dynamical systems would depend on the form of the
	systems derived in Section \ref{sec::Large_Agent_Dynamics} and it is likely that relaxations would
	be required in terms of controllability results. An example would be to examine only the
	behaviour in the long-enough time frame, which means that we could not impose a final time. Of
	course, this means that we could only consider optimal control rather than model predictive.
	However, without establishing the models from Section \ref{sec::Large_Agent_Dynamics}, this
	extension is speculative and it is likely that such an extension would fall outside the scope of
	the PhD.
